Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
typo

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of C programs 
to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
While they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented here in the
form of FWL effects and stability measures for LTI SISO controllers.
We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
from~\cite{daes20161}\todo{This paper seems to be for transfer functions, not state space,
is there a paper that does state space stability and safety?}
, while enhancing the procedure by evaluating the
quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
accurate discrete-time FWL representation of the continuous dynamics.

@@

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.

>>>>

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of software-implemented 
digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
technique, their approach is restricted to synthesising controllers for hybrid 
closed-loop systems that are stable and only consider transfer function models.  
In contrast, in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented here in the
form of FWL effects and stability measures for LTI SISO controllers.
We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
from~\cite{Monteiro16}%\todo{This paper seems to be for transfer functions, not state space,
%is there a paper that does state space stability and safety?}
, while enhancing the procedure by evaluating the
quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
accurate discrete-time FWL representation of the continuous dynamics.

@@

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
